---
title: "Digipur"
author: "Philipp Hölscher"
date: "2024-04-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = "/Users/philippholscher/Downloads/Masterthesis")
```


```{r}
getwd()
```



```{r setup, include=FALSE}
library(zoo)
library(dplyr)
library(tidyr)
library(purrr)
library(multivar)
library(mlVAR)
library(vars)
library(brms)
library(mgcv)
library(purrr)
library(otsfeatures)
library(SBC)
library(bayesplot)
library(ggplot2)
library(lubridate)
library(loo)
```
## Data Loading and Manipulation


```{r}
raw_data <- read.csv('20231006_DigiPuR_AA_data_KiJu.csv', sep=';', header=TRUE)
```

```{r}
KiJu_AA <- read.csv('20231006_DigiPuR_AA_data_KiJu.csv', sep=';', header=TRUE)

# Select only the specified columns
keep <- c('id', 'Start_date', 't70_k_k_sr_akad_5', 't70_k_k_sr_pos_1', 't70_k_k_sr_mv_8', 't70_k_k_schlaf_1', 't70_k_k_schlaf_2', 't70_k_k_wohlbefinden_1')
KiJu_AA <- KiJu_AA[, keep]
```


```{r}
get_mode <- function(x) {
  # Exclude NAs
  x <- na.omit(x)
  # Calculate the most frequent value
  uniq_vals <- unique(x)
  uniq_vals[which.max(tabulate(match(x, uniq_vals)))]
}

# Replace NA values with the mode
df <- KiJu_AA %>%
  group_by(id) %>%
  mutate(across(
    c('t70_k_k_sr_akad_5', 't70_k_k_sr_pos_1', 't70_k_k_sr_mv_8', 
      't70_k_k_schlaf_1', 't70_k_k_schlaf_2', 't70_k_k_wohlbefinden_1'),
    ~ ifelse(is.na(.), get_mode(.), .)
  )) %>%
  ungroup()
```


```{r}
nested_df <- lapply(split(df, df$id), function(group) {
  rownames(group) <- NULL  # Reset row names
  group[,]  # Remove 'id' column
})
```

```{r}
time_series_data <- list(list())
regression_data <- list(list())
```

```{r}
x <- 1
y <- 1
for (i in 1:length(nested_df)){
  dummy <- as.data.frame(nested_df[[i]])
  dummy <- subset(dummy,select = -Start_date)
  

  if (dim(dummy)[1]>20){
    
    time_series_data[[x]] <- dummy
    x <- x +1
  }else{
    
    regression_data[[y]] <- dummy
    y <- y +1
  }
}
```

## ACF
Let's investigate the ACF plots.
```{r}
acf(time_series_data[[1]][["t70_k_k_schlaf_2"]],lag=7)
```

## Model builduing
Adjust control settings to ensure proper convergence and avoid divergent trajactories.
```{r}
control <- list(
  adapt_engaged = TRUE,
  adapt_delta = 0.99, 
  stepsize = 0.05, # 0.05 default
  max_treedepth = 50
)
```


### Training
Simple Training Loop.
```{r}
for (i in (1:6)){#(1:length(time_series_data))
  train_data <- time_series_data[[i]]
  test_data <- train_data[21:length(train_data),1:7]
  train_data_sub <- train_data[1:20,1:7]
  save_data(train_data_sub,test_data,i)
  cum_fit <- trainloop_2(train_data_sub,control,name,i)
}
```



Safe Training Data.
```{r}
save_data <- function(train_data_sub,test_data,i){
  data_name <- paste0("train_data_sub/train_data_sub_", i, ".rds")
  file_path <- file.path(getwd(), data_name)
  saveRDS(train_data_sub,file=file_path)
  data_name2 <- paste0("test_data/test_data_", i, ".rds")
  file_path2 <- file.path(getwd(), data_name2)
  saveRDS(train_data_sub,file=file_path2)  
}
```

This function Trains the Time Series Models.
```{r}
trainloop <- function(train_data_sub,control,name,i){
  cum_fit <- brm(formula = mvbind(t70_k_k_sr_akad_5,t70_k_k_sr_pos_1,t70_k_k_sr_mv_8,t70_k_k_schlaf_1,t70_k_k_schlaf_2,t70_k_k_wohlbefinden_1)
 ~ ar(p = 1), data = train_data_sub, family=cumulative("cauchit")
  ,chains = 4,iter = 10000,warmup = 2000,init = '0',control=control)
  model_name <- paste0("models/cum_fit_", i, ".rds")
  file_path <- file.path(getwd(), model_name)
  saveRDS(cum_fit,file=file_path)
  return(cum_fit)
}
```

This function Trains the Mean Models.
```{r}
trainloop_2 <- function(train_data_sub,control,name,i){
  mean_model <- brm(formula = mvbind(t70_k_k_sr_akad_5,t70_k_k_sr_pos_1,t70_k_k_sr_mv_8,t70_k_k_schlaf_1,t70_k_k_schlaf_2,t70_k_k_wohlbefinden_1)
 ~ 1, data = train_data_sub, family=cumulative("cauchit")
  ,chains = 4,iter = 10000,warmup = 2000,init = '0',control=control)
  model_name <- paste0("models_mean/mean_model_", i, ".rds")
  file_path <- file.path(getwd(), model_name)
  saveRDS(mean_model,file=file_path)
  return(mean_model)
}
```

### Evaluation

This function gets the predictions.
```{r}
get_predictions <- function(cum_fit){
  predictions_prob <- posterior_predict(cum_fit)
  predictions <- as.data.frame(predictions_prob[1,1:20,1:6])
  return(predictions)
}
```



### Predictions and confuison matrix

This function creates confuison matrices.
```{r}
calculate_confusion_matrices <- function(predictions_sample, test_data, labels, value_names) {
  # Initialize an empty list to store confusion matrices
  confusion_matrices <- list()
  column_name <- colnames(test_data)
  
  # Iterate over each column in the test_data DataFrame
  for (i in 1:ncol(test_data)) { # Use ncol() to get the number of columns
    
    
    
    # Calculate the confusion matrix
    conf_matrix <- table(
      factor(predictions_sample[[i]], levels = labels),
      factor(test_data[[i]], levels = labels)
    )
    
    # Set the dimension names
    dimnames(conf_matrix) <- list(
      "Predicted" = value_names,
      "Actual" = value_names # Fix this to directly assign "Actual" as the label
    )
    
    # Save the confusion matrix in the list with the column name
    confusion_matrices[[column_name[i]]] <- conf_matrix
  }
  
  # Return the list of confusion matrices
  return(confusion_matrices)
}
```







This function iterates over the models and calls the confusion matrices function. Then saves the matrices.
```{r}
process_folders <- function(models_folder, data_folder, output_folder, labels, value_names) {
  # Create output folder if it doesn't exist
  if (!dir.exists(output_folder)) {
    dir.create(output_folder)
  }
  
  # Get lists of models and data files
  model_files <- list.files(models_folder, full.names = TRUE, pattern = "\\.rds$")
  data_files <- list.files(data_folder, full.names = TRUE, pattern = "\\.rds$")
  
  # Ensure corresponding files match in order
  if (length(model_files) != length(data_files)) {
    stop("The number of model files and data files must be the same.")
  }
  
  # Iterate over models and test data
  for (i in seq_along(model_files)) {
    # Load the model and test data
    model <- readRDS(model_files[i])
    test_data <- readRDS(data_files[i])
    
    test_data <- test_data[, !(names(test_data) %in% "id")]
    
    # Generate predictions
    predictions <- get_predictions(model)
    predictions <- predictions[1:dim(test_data)[1],]

    
    # Calculate confusion matrices
    confusion_matrices <- calculate_confusion_matrices(predictions, test_data, labels, value_names)
    
    # Save the confusion matrices as an RDS file
    output_file <- file.path(output_folder, paste0("confusion_matrix_", i, ".rds"))
    saveRDS(confusion_matrices, output_file)
    
    # Print progress
    cat("Saved confusion matrix for file", i, "to", output_file, "\n")
  }
}

```

Call the functions for mean models.
```{r}
# Example usage
models_folder <- "/Users/philippholscher/Downloads/Masterthesis/models_mean"  # Replace with your folder path
data_folder <- "/Users/philippholscher/Downloads/Masterthesis/test_data"      # Replace with your folder path
output_folder <- "/Users/philippholscher/Downloads/Masterthesis/confusion_matrix_mean"  # Replace with your folder path

labels <- c(1,2,3,4,5)
value_names <- c("Value 1", "Value 2", "Value 3", "Value 4", "Value 5")

process_folders(models_folder, data_folder, output_folder, labels, value_names)
```

Call the functions for AR models.
```{r}
# Example usage
models_folder <- "/Users/philippholscher/Downloads/Masterthesis/models"  # Replace with your folder path
data_folder <- "/Users/philippholscher/Downloads/Masterthesis/test_data"      # Replace with your folder path
output_folder <- "/Users/philippholscher/Downloads/Masterthesis/confusion_matrix"  # Replace with your folder path

labels <- c(1,2,3,4,5)
value_names <- c("Value 1", "Value 2", "Value 3", "Value 4", "Value 5")

process_folders(models_folder, data_folder, output_folder, labels, value_names)
```





## PPC 

Function iterates over models, calculates PPC and saves them.
```{r}
ppc_check_all_models <- function(input_folder, output_folder) {
  # Ensure output folder exists
  if (!dir.exists(output_folder)) {
    dir.create(output_folder, recursive = TRUE)
  }
  
  # List all .rds files in the input folder
  model_files <- list.files(input_folder, pattern = "\\.rds$", full.names = TRUE)
  
  # Define the response variables for pp_check
  response_vars <- c('t70kksrakad5', 't70kksrpos1', 't70kksrmv8', 
                     't70kkwohlbefinden1', 't70kkschlaf1', 't70kkschlaf2')
  
  # Iterate over each model file
  for (model_file in model_files) {
    # Load the model
    cum_fit <- readRDS(model_file)
    
    # Extract the base model name without path and extension
    model_name <- tools::file_path_sans_ext(basename(model_file))
    
    # Iterate over each response variable
    for (resp_var in response_vars) {
      # Generate the posterior predictive check plot
      pp_plot <- pp_check(cum_fit, resp = resp_var, ndraws = 1000, type = 'bars')
      
      # Create a unique filename for each plot
      plot_filename <- paste0(output_folder, "/", model_name, "_", resp_var, ".png")
      
      # Save the plot
      ggsave(plot_filename, plot = pp_plot, width = 8, height = 6)
    }
  }
  
  cat("Posterior predictive checks completed and saved in", output_folder, "\n")
}

```

Call function for AR models.
```{r}
#/Users/philippholscher/Downloads/Masterthesis/models
#/Users/philippholscher/Downloads/Masterthesis/ppc_check

ppc_check_all_models("/Users/philippholscher/Downloads/Masterthesis/models", "/Users/philippholscher/Downloads/Masterthesis/ppc_check")
```
Call function for mean models.

```{r}
ppc_check_all_models("/Users/philippholscher/Downloads/Masterthesis/models_mean", "/Users/philippholscher/Downloads/Masterthesis/ppc_check_mean")
```


## WAIC and LOO

Function calculates LOO comparison for mean models and AR counterparts and saves them.
```{r}
compare_models_to_df <- function(folder1, folder2) {
  # List all model files in both folders
  models_folder1 <- list.files(folder1, full.names = TRUE)
  models_folder2 <- list.files(folder2, full.names = TRUE)
  
  # Ensure the number of models matches
  if (length(models_folder1) != length(models_folder2)) {
    stop("The number of models in the two folders does not match!")
  }
  

  
  # Initialize lists to store loo objects and comparisons
  loo1_list <- list()
  loo2_list <- list()
  loo_comparisons <- list()
  
  # Iterate through models and compare
  for (i in seq_along(models_folder1)) {
    # Load models
    model1 <- readRDS(models_folder1[i])
    model2 <- readRDS(models_folder2[i])
    
    # Compute `loo` for both models
    loo1 <- loo(model1)
    loo2 <- loo(model2)
    
    # Save loo objects in their respective lists
    loo1_list[[i]] <- loo1
    loo2_list[[i]] <- loo2
    
    # Compare models
    loo_comparison <- loo_compare(loo1, loo2)
    
    # Save loo_comparison in the list
    loo_comparisons[[i]] <- loo_comparison
    


  }
  
  # Return the results and loo objects
  return(list(
    loo1_list = loo1_list,
    loo2_list = loo2_list,
    loo_comparisons = loo_comparisons
  ))
}

```



Call function.
```{r}
folder1 <- "/Users/philippholscher/Downloads/Masterthesis/models"
folder2 <- "/Users/philippholscher/Downloads/Masterthesis/models_mean"

# Get the comparison results as a data frame
comparison_results <- compare_models_to_df(folder1, folder2)

```


Print Loo Comparison.
```{r}
loo_comp_1 <- comparison_results[["loo_comparisons"]][[1]]
print(loo_comp_1,simplify = FALSE)
```

```{r}
confusion_matrix<- readRDS("/Users/philippholscher/Downloads/Masterthesis/confusion_matrix/confusion_matrix_1.rds")

confusion_matrix_mean<- readRDS("/Users/philippholscher/Downloads/Masterthesis/confusion_matrix_mean/confusion_matrix_1.rds")
```




```{r}
print(confusion_matrix)
```



```{r}
print(confusion_matrix_mean)

```


##### Logistic Regression

Data Preprocessing for Logistic Regression.
```{r}
regression_last_data <- map(regression_data, ~ .x[nrow(.x), ])
regression_last_data <- map(regression_last_data, ~ .x %>% ungroup()) %>%
  bind_rows()
```


```{r}
data_big <- read.csv('20231006_DigiPuR_final_data.csv', sep=';', header=TRUE)
```


```{r}
data_filtered_test <- subset(data_big,pers=='KiJu',select = c('id','date','t1_kd_alter','t1_kd_geschlecht','t1_kd_iq_wert','t1_kd_klassenwiederholungen','t4_kd_wiederauf_fu2'))
```




```{r}
data_cleaned <- data_filtered_test %>%
  group_by(id) %>%
  slice(1) %>%  # Keeps the first row in each group
  ungroup()
```


```{r}
train_data_regression <- regression_last_data %>%
  inner_join(data_cleaned, by = "id")
```

```{r}
train_data_regression$age <- as.Date(train_data_regression$t1_kd_alter, origin = "1899-12-30")
```

```{r}
train_data_regression <- train_data_regression %>%
  mutate(
    date = dmy(date),  
    age = ymd(age)  
  )
train_data_regression <- train_data_regression %>%
  mutate(
    age_at_start = round(as.numeric(difftime(date, age, units = "days")) / 365.25)
  )

```

```{r}
train_data_regression <- train_data_regression[, !(names(train_data_regression) %in% c("date", "age","t1_kd_alter"))]
```

```{r}
train_data_regression$t1_kd_klassenwiederholungen[is.na(train_data_regression$t1_kd_klassenwiederholungen)] <- 0
train_data_regression$t1_kd_geschlecht <- ifelse(train_data_regression$t1_kd_geschlecht == "m", 0, ifelse(train_data_regression$t1_kd_geschlecht == "w", 1, NA))
train_data_regression$t4_kd_wiederauf_fu2 <- ifelse(train_data_regression$t4_kd_wiederauf_fu2 == 4, 0, 1)

```

```{r}
train_data_regression$t1_kd_iq_wert <- log(train_data_regression$t1_kd_iq_wert)
train_data_regression$age_at_start <- log(train_data_regression$age_at_start)
```


```{r}
train_data_regression <- na.omit(train_data_regression)
```

```{r}
train_data_regression$t1_kd_iq_wert <- as.integer(train_data_regression$t1_kd_iq_wert)
```



### Model
Fit the different models and calculate LOO.
```{r}
final_model <- brm(formula = t4_kd_wiederauf_fu2 ~ t70_k_k_sr_pos_1 + t70_k_k_sr_akad_5 + t70_k_k_sr_mv_8 + t70_k_k_schlaf_1 + t70_k_k_schlaf_2 + t70_k_k_wohlbefinden_1,  
                   data=train_data_regression, 
                   family = bernoulli(link = "logit"),
                   warmup = 2000, 
                   iter = 15000,
                   init = '0' )
```

```{r}
summary(final_model)
```


```{r}
timeseries_loo <- loo(final_model)
```


```{r}
final_model_big <- brm(formula = t4_kd_wiederauf_fu2 ~ t70_k_k_sr_pos_1 + t70_k_k_sr_akad_5 + t70_k_k_sr_mv_8 + t70_k_k_schlaf_1 + t70_k_k_schlaf_2 + t70_k_k_wohlbefinden_1 +t1_kd_klassenwiederholungen,  
                   data=train_data_regression, 
                   family = bernoulli(link = "logit"),
                   warmup = 2000, 
                   iter = 15000,
                   init = '0')
```

```{r}
summary(final_model_big)
```


```{r}
timeseries_klassenwieder_loo <- loo(final_model_big)
```


```{r}
final_model_3 <- brm(formula = t4_kd_wiederauf_fu2 ~ t70_k_k_sr_pos_1 + t70_k_k_sr_akad_5 + t70_k_k_sr_mv_8 + t70_k_k_schlaf_1  + t70_k_k_wohlbefinden_1 +t1_kd_iq_wert + t1_kd_klassenwiederholungen,  
                   data=train_data_regression, 
                   family = bernoulli(link = "logit"),
                  warmup = 2000, 
                   iter = 15000,
                   init = '0')
```

```{r}
summary(final_model_3)
```


```{r}
timeseries_iq_klassenwieder_loo <- loo(final_model_3)
```



```{r}
variational_inference_model = brm(formula = t4_kd_wiederauf_fu2 ~ t70_k_k_sr_pos_1 + t70_k_k_sr_akad_5 + t70_k_k_sr_mv_8 + t70_k_k_schlaf_1 + t70_k_k_schlaf_2 + t70_k_k_wohlbefinden_1 + t1_kd_geschlecht+t1_kd_iq_wert + t1_kd_klassenwiederholungen +age_at_start,  
                   data=train_data_regression, 
                   family = bernoulli(link = "logit"),
                   warmup = 2000, 
                   iter = 15000,
                   init = '0',algorithm = "meanfield",chain=4 )
```


```{r}
summary(variational_inference_model)
```

```{r}
vi_loo <- loo(variational_inference_model,moment_match = TRUE,reloo = TRUE)
```



```{r}
loo_final_model <- loo_compare(vi_loo,timeseries_iq_klassenwieder_loo,timeseries_klassenwieder_loo,timeseries_loo)
```

Print LOO Comparison.
```{r}
print(loo_final_model,simplify = FALSE)
```
#### Test Model on Test Data



```{r}
test_pred <- get_predictions(cum_fit)
test_pred <- head(test_pred,1)
```

```{r}
new_names <- c(
  't70_k_k_sr_pos_1', 
  't70_k_k_sr_akad_5', 
  't70_k_k_sr_mv_8', 
  't70_k_k_schlaf_1', 
  't70_k_k_schlaf_2', 
  't70_k_k_wohlbefinden_1'
)
```


Function to get the logistic predictions.
```{r}
# Define the function
get_model_predictions_logistic <- function(folder_path, new_colnames, newdata_function) {
  # List all model files in the folder
  model_files <- list.files(folder_path, full.names = TRUE)
  
  # Initialize a list to store predictions
  predictions_list <- list()
  
  # Iterate over model files
  for (file in model_files) {
    # Load the model (assuming models are RData files with a single object named cum_fit)
    model <- readRDS(file)
    
    
    test_pred <- get_predictions(model)
    
    # Process the predictions (e.g., take the first row)
    test_pred <- head(test_pred, 1)
    
    # Rename columns
    colnames(test_pred) <- new_colnames
    
    # Generate predictions using the final model
    pred <- predict(final_model, newdata = test_pred)
    
    # Append predictions to the list
    predictions_list[[basename(file)]] <- pred
  }
  
  # Return the list of predictions
  return(predictions_list)
}

```

Call function with mean models.
```{r}
logistic_predictions <- get_model_predictions_logistic(folder_path ="/Users/philippholscher/Downloads/Masterthesis/models_mean",new_colnames =new_names ,newdata_function = get_predictions())
```

Bring predictions in nice format.
```{r}
id_list <- lapply(time_series_data, function(x) x$id)
id_vector <- unlist(id_list)
prediction_list <- lapply(logistic_predictions,function(x) round(x[1]))
id_list <- as.list(id_vector)
```



```{r}
df_final <- data.frame(
  id = rep(NA, 32),
  prediction = rep(NA, 32))
df_final$id <- id_vector
df_final$prediction <- prediction_list
```

```{r}
joined_df <- inner_join(df_final, data_filtered_test, by = "id")
```

```{r}
joined_df_cleaned <- joined_df %>%
  group_by(id) %>%
  slice(1) %>%  # Keeps the first row in each group
  ungroup()
```

```{r}
joined_df_cleaned <- joined_df_cleaned[, !(names(joined_df_cleaned) %in% c("date", "t1_kd_geschlecht", "t1_kd_alter","t1_kd_iq_wert","t1_kd_klassenwiederholungen","id"))]
```
Create Confusion Matrices
```{r}
joined_df_cleaned$t4_kd_wiederauf_fu2<- ifelse(joined_df_cleaned$t4_kd_wiederauf_fu2 == 4, 0, 1)
```


```{r}
conf_matrix_final <- table(unlist(joined_df_cleaned$prediction),joined_df_cleaned$t4_kd_wiederauf_fu2)
rownames(conf_matrix_final) <- c("Predicted 0", "Predicted 1")
colnames(conf_matrix_final) <- c("Actual 0", "Actual 1")
```

```{r}
conf_matrix_final
```
PPC for Logistic Model.
```{r}
pp_check(final_model,type='bars')
```






```{r}
model_ar <- readRDS('/Users/philippholscher/Downloads/Masterthesis/models/cum_fit_1.rds')
model_mean <- readRDS('/Users/philippholscher/Downloads/Masterthesis/models_mean/mean_model_1.rds')
```




```{r}
summary(model_mean)
```

```{r}
summary(final_model)
```


