---
title: "R Notebook"
output: html_notebook
---

```{r}
library(brms)
library(dplyr)
library(rstan)
library(sbc)
```

## Simulation-Based Calibration

#### Generate Data

To perform the SBC we need an artificial data set so the function knows the structure of the data.

```{r}
set.seed(213452)
template_data = data.frame( t70kksrakad5 = rep(2, 15),t70kksrpos1 = rep(1, 15),t70kksrmv8 = rep(3, 15), t70kkschlaf1 = rep(4, 15), t70kkschlaf2 = rep(5, 15),t70kkwohlbefinden1 = rep(3, 15))
```

#### Priors

Define the priors of the models, for sampling.

```{r}
priors_mean <- c(
    prior(student_t(3, 0, 2.5), class = "Intercept", resp = "t70kkschlaf1"),
    prior(student_t(3, 0, 2.5), class = "Intercept", resp = "t70kkschlaf2"),
    prior(student_t(3, 0, 2.5), class = "Intercept", resp = "t70kksrakad5"),
    prior(student_t(3, 0, 2.5), class = "Intercept", resp = "t70kksrmv8"),
    prior(student_t(3, 0, 2.5), class = "Intercept", resp = "t70kksrpos1"),
    prior(student_t(3, 0, 2.5), class = "Intercept", resp = "t70kkwohlbefinden1")
)
```

```{r}
priors <- c(
  prior(uniform(-1,1), class = "ar", resp = "t70kkschlaf1",lb=-1,ub=1),
  prior(uniform(-1,1), class = "ar", resp = "t70kkschlaf2",lb=-1,ub=1),
  prior(uniform(-1,1), class = "ar", resp = "t70kksrakad5",lb=-1,ub=1),
  prior(uniform(-1,1), class = "ar", resp = "t70kksrmv8",lb=-1,ub=1),
  prior(uniform(-1,1), class = "ar", resp = "t70kksrpos1",lb=-1,ub=1),
  prior(uniform(-1,1), class = "ar", resp = "t70kkwohlbefinden1",lb=-1,ub=1),
  prior(student_t(3, 0, 2.5), class = "Intercept", resp = "t70kkschlaf1"),
  prior(student_t(3, 0, 2.5), class = "Intercept", resp = "t70kkschlaf2"),
  prior(student_t(3, 0, 2.5), class = "Intercept", resp = "t70kksrakad5"),
  prior(student_t(3, 0, 2.5), class = "Intercept", resp = "t70kksrmv8"),
  prior(student_t(3, 0, 2.5), class = "Intercept", resp = "t70kksrpos1"),
  prior(student_t(3, 0, 2.5), class = "Intercept", resp = "t70kkwohlbefinden1")
)
```

### SBC

Here we create datagenerators by combining the artificial data set and the defined priors.

```{r}
set.seed(213452)


generator <- SBC_generator_brms(mvbind(t70kksrakad5,t70kksrpos1,t70kksrmv8,t70kkschlaf1,t70kkschlaf2,t70kkwohlbefinden1)
 ~ ar(p = 1), data = template_data, prior = priors, 
                                thin = 50, warmup = 1000, refresh = 200)
```

```{r}
set.seed(213452)


generator_mean <- SBC_generator_brms(mvbind(t70kksrakad5,t70kksrpos1,t70kksrmv8,t70kkschlaf1,t70kkschlaf2,t70kkwohlbefinden1)
 ~ 1, data = template_data, prior = priors_mean, 
                                thin = 50, warmup = 1000, refresh = 200)
```

Now we generate the artificial data set.

```{r}
datasets <- generate_datasets(generator, 100)
```

```{r}
datasets_mean <- generate_datasets(generator_mean, 100)
```

Now we create a so-called backend, that is later used with the generated artificial data set to perform the actual SBC.

```{r}
backend <- SBC_backend_brms_from_generator(generator, chains = 1, thin = 1,
                            warmup = 500, iter = 1500,               
                            inits = 0.1)
```

```{r}
backend_mean <- SBC_backend_brms_from_generator(generator_mean, chains = 1, thin = 1,
                            warmup = 500, iter = 1500,               
                            inits = 0.1)
```

SBC is being computed.

```{r}
results_mean <- compute_SBC(datasets_mean, backend_mean)
```

```{r}
results <- compute_SBC(datasets, backend)
```

### Results

Visualize the Results.

```{r}
plot_rank_hist(results_mean)
```

```{r}
plot_rank_hist(results)

```

```{r}
plot_ecdf_diff(results)

```

```{r}
plot_ecdf_diff(results_mean)
```
